\section{}





\begin{lemma}
  Let~$F \colon \Acat \to \Bcat$ be an exact functor between abelian categories~$\Acat$ and~$\Bcat$.
  Then~$F$ respects exact sequences, i.e.\ if
  \[
    X'
    \xlongto{f}
    X
    \xlongto{g}
    X''
  \]
  is an exact sequence in~$\Acat$, then the resulting sequence
  \[
    F(X')
    \xlongto{F(f)}
    F(X)
    \xlongto{F(g)}
    F(X'')
  \]
  in~$\Bcat$ is again exact.
\end{lemma}


\begin{proof}
  It follows from the exactness of the functor~$F$ that it is both left exact and right exact.
  Hence~$F$ respects both kernels and cokernels.
  Therefore~$F$ respect both images and coimages.
  We have that
  \[
      F(g) \circ F(f)
    = F(g \circ f)
    = F(0)
    = 0
  \]
  because~$F$ is additive, and we find from the above discussion that the induced canonical morphism~$\im(F(f)) \to \ker(F(g))$ in~$\Bcat$ is given by the image of the canonical morphism~$\im(f) \to \ker(g)$ in~$\Acat$ under the functor~$F$.
  Since~$\im(f) \to \ker(g)$ is an isomorphism the same follows for~$\im(F(f)) \to \ker(F(g))$ (because the functor~$F$ respects isomorphisms).
\end{proof}


\begin{corollary}
  If~$F \colon \Acat \to \Bcat$ is an exact functor between abelian categories~$\Acat$ and~$\Bcat$, then for every long exact sequence
  \[
    \dotsb
    \to
    X_{i-1}
    \to
    X_i
    \to
    X_{i+1}
    \to
    \dotsb
  \]
  in~$\Acat$ the resulting sequence
  \[
    \dotsb
    \to
    F(X_{i-1})
    \to
    F(X_i)
    \to
    F(X_{i+1})
    \to
    \dotsb
  \]
  in~$\Bcat$ is again exact.
  \qed
\end{corollary}

We find that if~$\Tdeltac \colon \Acat \to \Bcat$ is a cohomological~{\deltafun} given by
\[
  \Tdeltac
  =
  ( (T^n)_{n \geq 0}, (\delta^n_\xi)_{n \geq 0, \xi} )
\]
and if~$F \colon \Bcat \to \Ccat$ is an exact functor, where~$\Acat$,~$\Bcat$ and~$\Ccat$ are abelian categories, then
\[
  F \circ \Tdeltac
  \defined
  ( (F \circ T^n)_{n \geq 0}, (F(\delta^n_\xi))_{n \geq 0, \xi} )
\]
is a~{\deltafun}~$\Acat \to \Ccat$.
If the category~$\Acat$ has enough injectives and~$\Tdeltac$ is universal, then~$F \circ \Tdeltac$ is again universal.
This holds because the~{\deltafuns}~$\Tdeltac$ and~$F \circ \Tdeltac$ are universal if and only if the functors~$T^n$ (resp.~$F \circ T^n$) annihilate all injective objects for every~$n \geq 1$.

We are now prepared for the exercise:
The functor~$G \circ F$ is again left exact because both~$G$ and~$F$ are left exact.
We find that~$G \circ (\Rightdelta F)$ is a cohomological~{\deltafun}~$\Acat \to \Ccat$ with~$G \circ T^0 \cong G \circ F$ because~$T^0 \cong F$.
The~{\deltafun}~$\Rightdelta F$ is universal, and hence~$G \circ (\Rightdelta F)$ are universal as seen above.





