\section{}





\subsection{}

The sequence
\[
  \Hom_\Acat(X, Y')
  \xlongto{h^X(f)}
  \Hom_\Acat(X, Y)
  \xlongto{h^X(g)}
  \Hom_\Acat(X, Y'')
\]
is precisely the sequence
\[
  Y'(X)
  \xlongto{f}
  Y(X)
  \xlongto{g}
  Y''(X)
\]
of~\dash{$X$}{valued} points.
The statement follows from this observation because exactness can be computed on (generalized) points (see Theorem~3.42).





\subsection{}

We show that the functor~$F$ respects finite coproducts; that~$F$ is additive then follows from Theorem~3.24.
It can then also be shown dually that the functor~$G$ respects finite products, which then also shows that~$G$ is additive.

Let~$(C, (c_1, \dotsc, c_n))$ be a coproduct of finitely many objects~$X_1, \dotsc, X_n$ of~$\Acat$.
Then
\[
  \Hom_\Bcat(F(C), -)
  \cong
  \Hom_\Acat(C, G(-))
  \cong
  \prod_{i=1}^n \Hom_\Acat(X_i, G(-))
  \cong
  \prod_{i=1}^n \Hom_\Bcat(F(X_i), -) \,.
\]
This shows that the object~$F(C)$ represents the functor~$\prod_{i=1}^n \Hom_\Bcat(F(X_i), -)$.
This means that the object~$F(C)$ becomes a coproduct of the objects~$F(X_1), \dotsc, F(X_n)$ with respect to suitable morphisms~$c'_i \colon F(X_i) \to F(C)$.
Such morphisms~$c'_1, \dotsc, c'_n$ can be determined via the above isomorphism of functors:
The identity
\[
  \id_{F(C)}
  \in
  \Hom_\Bcat(F(C), F(C))  \,.
\]
corresponds under the above isomorphism to the one such tupel
\[
  (c'_1, \dotsc, c'_n)
  \in
  \prod_{i=1}^n \Hom_\Bcat(F(X_i), F(X))  \,.
\]
Under the above isomorphisms we have
\[
  \id_{F(C)}
  \mapsto
  \varphi(\id_{F(C)})
  \mapsto
  ( \varphi(\id_{F(C)}) \circ c_i )_{i=1}^n
  \mapsto
  ( \varphi^{-1}(\varphi(\id_{F(C)}) \circ c_i) )_{i=1}^n \,,
\]
and hence
\[
  c'_i
  =
  \varphi^{-1}(\varphi(\id_{F(C)}) \circ c_i)
\]
for every~$i$.
To show that~$F$ respects the given coproduct we need to show that~$c'_i = F(c_i)$ for every~$i$, and hence that
\[
  F(c_i)
  =
  \varphi^{-1}(\varphi(\id_{F(C)}) \circ c_i)
\]
for every~$i$.

We recall that for all composable morphisms
\[
  F(X)
  \xlongto{f}
  Y
  \xlongto{g}
  Y'
\]
in~$\Bcat$ we have the identity
\[
  \varphi(g \circ f)
  =
  G(g) \circ \varphi(f) \,,
\]
and that for all composable morphisms
\[
  X
  \xlongto{f}
  X'
  \xlongto{g}
  G(Y)
\]
in~$\Acat$ we have the identity
\[
  \varphi^{-1}(g \circ f)
  =
  \varphi^{-1}(g) \circ F(f) \,.
\]
We find with this second identity the desired equality
\[
  \varphi^{-1}(\varphi(\id_{F(C)}) \circ c_i)
  =
  \varphi^{-1}(\varphi(\id_{F(C)})) \circ F(c_i)
  =
  \id_{F(C)} \circ F(c_i)
  =
  F(c_i) \,.
\]





\subsection{}

We show that the right adjoint functor~$G$ is left exact.
The right exactness of~$F$ then follows by duality.

We need to show that for every short exact sequence
\[
  0
  \to
  Y'
  \to
  Y
  \to
  Y''
  \to
  0
\]
in~$\Bcat$ the resulting sequence
\[
  0
  \to
  G(Y')
  \to
  G(Y)
  \to
  G(Y'')
\]
in~$\Acat$ is again (left) exact.
We use part~(i) of this exercise, and show that for every object~$X$ of~$\Acat$ the resulting sequence
\[
  \Hom_\Acat(X,0)
  \to
  \Hom_\Acat(X,G(Y'))
  \to
  \Hom_\Acat(X,G(Y))
  \to
  \Hom_\Acat(X,G(Y''))
\]
is exact.
We have that~$0 = G(0)$ because the functor~$G$ is additive, and hence need to show that the sequence
\[
  \Hom_\Acat(X,G(0))
  \to
  \Hom_\Acat(X,G(Y')
  \to
  \Hom_\Acat(X,G(Y))
  \to
  \Hom_\Acat(X,G(Y''))
\]
is exact.
This sequence is via the natural isomorphism~$\varphi$ isomorphic to the sequence
\[
  \Hom_\Bcat(F(X),0)
  \to
  \Hom_\Bcat(F(X),Y')
  \to
  \Hom_\Bcat(F(X),Y)
  \to
  \Hom_\Bcat(F(X),Y'') \,,
\]
which is the same as the sequence
\[
  0
  \to
  \Hom_\Bcat(F(X),Y')
  \to
  \Hom_\Bcat(F(X),Y)
  \to
  \Hom_\Bcat(F(X),Y'') \,.
\]
This sequence is indeed (left) exact---as desired---by the left exactness of the functor~$\Hom_\Bcat(F(X),-)$.






